
---
title: "Defects"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Libraries


we will need the following libraries: fitdistrplus, magrittr
```{r libraries, include=FALSE,echo=FALSE}
library(knitr)
library(fitdistrplus)
library(magrittr)

```

----------------------------A-D-----------------------------------------

#The Data of the mullfunctions arrivals

```{r}
#  defects_AD_table <- read_excel("C:/Users/yaronnak/Downloads/defects AD.xlsx", 
#     col_names = FALSE)

filePathAD <- choose.files()
tableAD <- read.csv(filePathAD,header=FALSE)
```
## 1.  Empirical Data

We will check if we have any outliers with boxplot function:

```{r}
defectsAD <- tableAD$V2
boxplot(defectsAD)
```

## 2. First Impressions 

We will do histogram for the data:
```{r}
hist(defectsAD, ylab="Frequency ") # histogram (right graph)
```

## 3. Fit a known distribution 

Now we will use R to estimate the paramters of known distribution to our data:
```{r}
normFit <- fitdist(defectsAD, "norm")
summary(defectsAD) # summary function displays the results 
```

Now we will use plotdist to plot our data versus the theoretical distribution 
```{r}
plotdist(defectsAD,"norm",para=list(mean=normFit$estimate[1],sd=normFit$estimate[2])) 
print(normFit)
```

## 4. Perform Goodness of Fit tests on fitted distribution

now that we got the fitting dist, will do statisticlly test the hypothesis our data came from this distribution.
we use Goodness of Fit tests (GOF).For that we will use Kolmogorov-Smirnov (KS).
We will use the general function gofstat:

```{r}
normGof <- gofstat(normFit)%>%print()
normGof$kstest%>%print()
```

#-------------------------------------------------E-J----------------------------------

```{r}

filePathEJ <- choose.files()
tableEJ <- read.csv(filePathEJ,header=FALSE)
```

## 1.  Empirical Data

  We will check if we have any outliers with boxplot function:

```{r fitting norm}
defectsEJ <- tableEJ$V2
boxplot(defectsEJ)

```

  will sort out all the valuse that is > 400
  and check with box plot agian

```{r}

new_defectsEJ <-   defectsEJ[which(defectsEJ<400)]
boxplot(new_defectsEJ)

```



# 2. First Impressions 

We will do histogram for the data:
```{r}
hist(new_defectsEJ, ylab="Frequency ") # histogram (right graph)
```


## 3. Fit a known distribution 

Now we will estimate the paramters of known distribution to our data:
```{r}
expFit <- fitdist(new_defectsEJ,"exp") 
summary(new_defectsEJ) # summary function displays the results 
```


Now we will use plotdist to plot our data versus the theoretical distribution 
```{r}
plotdist(new_defectsEJ,"exp",para=list(rate=expFit$estimate[1])) 
print(expFit)
```

## 4. Perform Goodness of Fit tests on fitted distribution

now that we got the fitting dist, will do statisticlly test the hypothesis our data came from this distribution.
samr as the previuse test, we use Goodness of Fit tests (GOF).For that we will use Kolmogorov-Smirnov (KS).
We will use the general function gofstat:

```{r}
expgof <-  gofstat(expFit)%>%print()
expgof$kstest%>%print()
```











